Compiling list of medications based on BNF codes for dementia/AD & palliative care drugs

### 2024-05-08 compile_medications_from_bnf.Rmd
added codes for injectable buscopan, accidentally included hyoscine hydrobromide (not buscopan) - but I dealt with this in the safe haven

One source for a list of all BNF codes is the Information Services Portal of the NHS Business Services Authority, https://applications.nhsbsa.nhs.uk/infosystems/data/showDataSelector.do?reportId=126. This is available after putting in a captcha-like password, so I've downloaded the file manually.

@@

@@

write_csv(bnf_palliative, file = "./bnf/bnf_codes_palliative_anticipatory.csv")
```

>>>>

One source for a list of all BNF codes is the [Information Services Portal of the NHS Business Services Authority] (https://applications.nhsbsa.nhs.uk/infosystems/data/showDataSelector.do?reportId=126). This is available after putting in a captcha-like password, so I've downloaded the file manually.

@@

## Buscopan/Hyoscine Butylbromide injections

In conversation with Jo Bowden, Sarah Mills, Sarah Bowers, we discussed using injectable buscopan/hyoscine butylbromide as a marker of palliative care.

```{r}
bnf_buscopan <-
  bnf %>%
  filter(str_detect(
    string = bnf_chemical_substance,
    pattern = regex("hyoscine", ignore_case = TRUE)
  )) %>% filter(str_detect(bnf_presentation, pattern = regex("inj", ignore_case = TRUE))) %>%
  select(bnf_section, bnf_section_code, bnf_product, bnf_presentation, bnf_presentation_code)
```

@@

write_csv(bnf_palliative, file = "./bnf/bnf_codes_palliative_anticipatory.csv")

write_csv(bnf_buscopan, file = "./bnf/bnf_codes_buscopan.csv")
```
